Formalizing Stack Safety as a Security Property

### 2022-10-20 submission5/noexceptions.tex
more comments on I-V

\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    Max Planck Institute for Security and Privacy\\
    roberto.blanco@mpi-sp.org\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce,
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
  }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}

@@

We state our properties in terms of a generic machine subject to a few constraints,
but our examples and tests are focused on a RISC-V-like machine enhanced with PIPE,
a tag-based reference monitor. Importantly, such a machine has no explicit ``call''
instruction, only {\tt jal} instructions which may be used for that purpose or potentially
other purposes. Similarly, there is no ``return'', only {\tt jalr}, and so on.
We therefore define our properties under the assumption that we can distinguish the
steps that represent these abstract operations from those that do not -- for instance,
by labeling instructions as calls, returns, etc. Such a labeling scheme appears in
our testing environment (Section [TBD]) and is already necessary
to correctly apply tag-based enforcement in practice (cite something about this.)

@@

We must trust that our method of distinguishing security operations is accurate; if it
involves labels placed on code by a compiler, that means trusting that the compiler placed
those labels correctly. If operations occur that are not recognized, those operations
might not be guaranteed to protect their principals -- for instance, an unlabeled call
might not protect the caller's data from the callee. On the flip side, applying an incorrect
label most likely means that the property becomes too strong to be enforced.

Otherwise, we do not assume that the code is reasonable or derived from any particular
calling convention or source construct. In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism may place additional constraints, of course, particularly on the behavior of
call and return sequences.

@@

Security operations consist of calls (including tailcalls), returns,
allocations and deallocations. Calls and tailcalls identify the address of the call's target,
and the argument registers. Allocations and deallocations are phrased in terms of a pair
of an offset from the stack pointer and a size. Returns don't require any additional information.
%
\begin{align*}
  \psi \in \Psi ::= & \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{tailcall} ~ \addr_{target}  ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{return} & \\
  | & \mathbf{alloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
  | & \mathbf{dealloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
\end{align*}
%
Security principals are function activations: at any given time, pending activations
have security requirements that are recorded in a call stack, and the current
activation tracks context information that will inform its requirements when
it makes a call. Each activation has a {\it view}
of the system that maps each state element to a{\it security classe}:
\[sc \in SEC ::= \sealed | \unsealed | \object | \public\]
\[V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\]

@@

\judgmenttwo{\(\mach \xrightarrow{\overline{\psi}} \mach', \obs \)}
            {\(\mathit{foldl} ~ (Op ~ \mach) ~ \context ~ \overline{\psi} = \context'\)}
            {\((\mach,\context) \stepstounder{\overline{\psi}} (\mach', \context'' \obs)\)}

\section{Calls, Returns, and Private Allocations}

In this section we consider a simple setting with calls, returns, and private allocations.
Figure \ref{fig:main} gives a C function {\tt main}, and its compiled RISC-V code,
that takes a secret in its arguments and initializes a variable to contain
potentially sensitive data.
It then calls another function {\tt f},
and afterward may decide to {\tt publish} its secret based on the contents of
its sensitive data. In this case, since {\tt sensitive} is initialized to 0,
it should not -- instead it will publish the results of {\tt f}.

@@

Suppose that {\tt f} is not a (valid) C function at all, but an attacker seeking
to leak {\tt secret}! It might do so in a number of ways, shown as snippets of
assembly code in Figure \ref{fig:f}.
In Figure \ref{subfig:direct}, {\tt f} takes an offset from the stack
pointer, access {\tt secret}, and directly call {\tt publish} itself. But more
subtly, even if somehow prevented from outputting {\tt secret} directly, {\tt f}
instead return that value so that {\tt main} makes the call to {\tt publish},
as in Figure \ref{subfig:indirect}.

@@

At the start of execution the program counter is 0 and the stack pointer -4, with the
stack growing down. The functions {\tt f} and {\tt publish}
are at addresses 100 and 200, respectively.

Figure \ref{fig:exec1} shows how the program counter, stack pointer, and context
develop over several steps, with labels on the steps that allocate space and then make
a call. \(\downarrow \overline{\psi}\) in this diagram is a sideways
\(\xrightarrow{\overline{\psi}}\). Events are omitted.

@@

On a call, the formerly active principal's record is pushed onto the inactive list.
Its return target is the return address of the call, 
and the stack pointer target is the stack pointer at the moment of call.
The callee's view is updated from the caller's such that all \(\object\) locations
become \(\sealed\). (In more complex settings, objects that are intentionally passed
to the callee will not get sealed, but for now we assume no sharing of memory.)
For registers, \(\overline{\reg_{args}}\) tells us which registers are used as arguments,
in this case {\tt a0}. These are mapped to \(\public\), while any non-argument, caller-saved
registers are mapped to \(\unsealed\). All callee-save registers are always \(\sealed\) and
the program counter \(\public\), as they were initialized.

On step \(n\), {\tt f} returns, and we restore the topmost inactive principal,
{\tt main}'s principal.

@@

But what if {\tt f} returns to an unexpected place (i.e. \(\PCname \neq 20\) or \(\SP \neq -24\)),
as would be the case in attack (d)? Then it has violated the WBCF property.
This property can be phrased in terms of a single step: for every transition
labeled as a return, the program counter and stack pointer at the next state
match those recorded in the top pending activation. The table in Figure \ref{fig:exec1}
assumes that WBCF is followed.

@@

In the case of the call from {\tt main} to {\tt f}, the \(\sealed\) elements are the
addresses -20 through -1 (allocated as private data) and callee-saved registers such as
the stack pointer and return address.
Note that the callee-saved registers may well have changed during the call -- but if
so, the callee is obligated to restore them to their prior value.

One further caveat: it is possible that {\tt f} might overwrite {\tt main}'s data
in a way that is harmless -- or that is rendered harmless by the enforcement mechanism!
This is the case in a lazy micro-policy: the monitor permits the caller to write into the
callee's frame, but taints that write so that the callee cannot read it later without
triggering a failstop. In such a scenario we will consider a value {\it irrelevant}
if it could be replaced with any other value without changing the observable behavior
of the machine. More precisely, for a given state \(\mach\) and set of elements \(\components\),
we define a {\em \(\components\)-variant} state to be one agrees with \(\mach\) on every
element except those in \(\components\). The elements of \(\components\) are said to be
irrelevant in \(\mach\) if every variant state produces an equivalent trace
(see Section \ref{sec:events}.)

@@

Returning to our example: at step 4, when {\tt main} makes its call to {\tt f},
the call stack in the context is empty. It makes its call, and at step 5, {\tt main}'s
frame, including {\tt secret} and {\tt sensitive}, is mapped to \(\sealed\) from the
perspective of {\tt f}. So, the next time the call stack is empty (implicitly, when
we have returned to {\tt main}), elements of that frame must either match their
values at step 4, or be irrelevant to future computation.

@@

We treat confidentiality as a form of non-interference as well: the confidentiality of a caller
means that its callee's behavior is dependent only on publicly visible data,
not the caller's private state. As we saw in the examples, we must consider both the observable events
that the callee produces during the call and the changes that the callee makes to the state that might
affect the caller after the callee returns.

@@

Together, these definitions encompass the confidentiality of the caller from the callee.

@@

The forms of stack safety described above are largely independent of one another, and
can potentially be enforced separately in various combinations. This is important, because
many enforcement mechanisms already in existence only enforce some of the stack safety
properties. Stricter enforcement may have greater performance impacts, leading to decisions
about trade-offs between different degrees of stack safety.

@@

Others combine this protection with some degree of memory protection,
chiefly focusing on integrity. Skorstengaard et al. \cite{SkorstengaardSTK} characterize stack
safety as the combination of WBCF and {\it local state encapsulation} (LSE), and prove that their
capability-based enforcement satisfies both. LSE corresponds to integrity, plus some degree of
confidentiality. They offer a fully abstract overlay semantics, which formalizes WBCF and LSE
together as a safe-by-construction abstract machine. That machine does not allow a callee to
read or write its caller's frame, but might allow it to read data that is left behind below
the caller's frame, which is weaker than our full caller confidentiality and rules out
callee confidentiality entirely. Georges et al. \cite{Georges22:TempsDesCerises} correct
both limitations.

@@

The intuition behind integrity (below) is that a caller may expect its
sealed data to be unchanged when control returns to it. In fact, the callee
may overwrite such data -- when the data are found in callee-saved registers
this is perfectly legal -- as long as it either restores it, or has some guarantee
that its changes will not impact the caller.

We start by defining a second-order logical operator
\(d \uparrow P\), read ``\(P\) holds on return from depth \(d\),''
where \(P\) is a predicate on machine states. This is a coinductive relation
similar to ``weak until'' in temporal logic -- it holds if the program never
returns from depth \(d\).

@@

Similarly, in confidentiality, we will want to compare pairs of future states,
so we give a binary equivalent, \(d \Uparrow R\), so that
\((\mach,\context) ~ (d \Uparrow R) ~ (\mach',\context')\) holds if \(R\) holds on the
first states that return from depth \(d\) after \((\mach,\context)\) and \((\mach',\context')\).
Once again, \(\Uparrow\) is coinductive.

@@

We now finally have everything we need to offer our definitions for stack safety.
Figure \ref{fig:oprules} gives the operation rules for all of the operations we've described
so far.

@@

\definition A system enjoys well-bracketed control flow if, for all states
\((\mach,(\_,(\_,\addr_{ret},\addr_{sp})) \stepstounder{\mathbf{return}} (\mach',\context,\obs)\),
\(\mach'[\PCname] = \addr_{ret}\) and \(\mach'[\SP] = \addr_{sp}\).

@@

Consider again the attack in Figure \ref{subfig:WBCF}: the attacker adds
20 to the return address and then returns, thus bypassing the check and publishing
{\tt secret}. During the call step, we record in the context that the return to the
caller should have the program counter at the next instruction (address 20) and the
stack pointer restored to address -20. When the return occurs, we see that in the
state following it, the program counter is 40 -- a violation of WBCF.

To demonstrate why WBCF also cares about the stack pointer, consider an attack which
returns with the stack pointer at -12. Now, compare the layout of the stack relative
to the stack pointer as it should be (top) to the one that results by increasing the
stack pointer before return (bottom):

@@

@@

Alternatively, we can formalize well-bracketed control flow using \(\uparrow\).

\definition For a machine state \(\mach\), let
\(ret ~ (\mach,\context) = \{\mach' | \mach'[\SP] = \mach[\SP] \land \mach'[\PCname] = \mach[\PCname]\}\).
A system enjoys well-bracketed control flow if, for all states 
\((\mach,\context) \stepstounder{\overline{\psi}} (\mach',(V,\sigma),\obs)\) with
\(\mathbf{call} ~ \addr ~ \overline{\reg} ~ \overline{sa} \in \psi\) or
\(\mathbf{tailcall} ~ \addr ~ \overline{\reg} ~ \overline{sa} \in \psi\),
\(|\sigma| \uparrow ret(\mach')\).

@@

Once again we can think about our example attack. When the call occurs,
we define a predicate \(ret ~ (\mach,\context)\) on states that holds when the program counter
and stack pointer have the appropriate values. Then we use apply the \(\uparrow\)
operator to this predicate with the depth of the call stack {\it after the call} and
the machine state {\it before the call}.

After the call, the call stack is one higher than it was before the call,
and if the callee makes further calls, it will continue to be incremented.
Each return will similarly decrement it, until it is finally lower than the
initial state. This is the return that matches the original call, and so
the resulting state is when we require \(ret(\mach)\) to hold.

@@

\definition Let \((\mach,\context)\) be a combined state with
\(\context = (V,\sigma)\), and
\(\components = \{\component | V ~ \component = \sealed\}\).
Let \(P ~ (\mach',\context')\) be a predicate that holds on a state
\(\Delta(\mach,\mach')\) is irrelevant in \((\mach', \context')\).
Then \(\mach\) enjoys {\it return-time integrity} if \(|\sigma| \uparrow P\) holds
on \((\mach,\context)\).

@@

\definition The {\em corrupted set} \(\bar{\Diamond}(\mach,\mach',\nach,\nach')\)
of four states treats \(\mach\) and \(\nach\) as the initial states and
\(\mach'\) and \(\nach'\) as their corresponding final states, and is the
set of elements that were corrupted between them. That is, the set of all elements
\(\component \in \Delta(\mach,\mach') \cup \Delta(\nach,\nach')\) such that
\(\mach'[\component] \not = \nach'[\component]\).

\definition Let \((\mach,\context)\) be a state with \(\context = (V,\sigma)\), and
\(\components = \{\component | V ~ \component \in \{\sealed, \unsealed\}\}\).

Then \((\mach,\context)\) enjoys {\it internal confidentiality} with respect to
if, for any \(\nach\) that is a \(\components\)-variant of \(\mach\), we can take
\(|\sigma| \uparrow (\mach,\context) \hookrightarrow \obsT\) and
\(|\sigma| \uparrow (\nach,\context) \hookrightarrow \obsT'\) and have that
\(\obsT \simeq \obsT'\).

\definition Let \((\mach,\context)\) be a state with \(\context = (V,\sigma)\),
and \(\components = \{\component | V ~ \component \in \{\sealed, \unsealed\}\}\).
Let \(\nach\) be a \(\components\)-variant of \(\mach\).
Let \(R\) be a relation such that \((\mach_1,\context_1) ~ R ~ (\mach_2,\context_2)\)
if \(\bar{\Diamond}(\mach,\mach_1,\nach,\mach_2)\) is irrelevant in \((\mach_1,\context_1)\).
Then \((\mach,\context)\) enjoys {\it return-time confidentiality}
if, for any such \(\nach\), \((\mach,\context) ~ (|\sigma| \Uparrow R) ~ (\nach,\context)\).

@@

\definition Let \((\mach,\context)\) be a state with \(\context = (V,\sigma)\), and
\(\components = \{\component | V ~ \component = \unsealed\}\).
Let \(P\) be a predicate that holds on a state \((\mach',\context')\) if
\(\mach' ~ \parallel ~ \Delta(\mach,\mach') \cap \components\).
Then \(\mach\) enjoys {\it post-return confidentiality} if \(|\sigma| \downarrow P\) holds.

@@

When the callee in such a scenario makes a call of its own, the objects passed to it
will in turn be sealed -- unless it passes them on, which can happen with pass-by-reference
arguments!

@@

In order to express such a property, we need our machine to carry some notion
of {\it pointer provenance} -- a distinction between a pointer that is intended to
point to a given object, and non-pointer integers as well as pointers to other objects.
Then \(\mathit{passed}\) should recursively identify all objects that
are reachable transitively from valid pointers in registers and accessible memory;
these keep their \(\object\) status, while those that are not reachable become \(\sealed\).

>>>>

\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    Max Planck Institute for Security and Privacy\\
    roberto.blanco@mpi-sp.org\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
  }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}

@@

We state our properties in terms of a generic machine subject to a few constraints,
but our examples and tests are focused on a RISC-V-like machine enhanced with PIPE,
a tag-based reference monitor. Importantly, such a machine has no explicit ``call''
instruction, only {\tt jal} instructions which may be used for that purpose or potentially
other purposes. Similarly, there is no ``return'', only {\tt jalr}, and so on.
We therefore define our properties under the assumption that we can distinguish the
steps that represent these abstract operations from those that do not---for instance,
by labeling instructions as calls, returns, etc.\apt{note proper way to do punctuating dashes}
Such a labeling scheme appears in
our testing environment (Section [TBD]) and is already necessary
to correctly apply tag-based enforcement in practice (cite something about this.)

@@

We must trust that our method of distinguishing security operations is accurate; if it
involves labels placed on code by a compiler, that means trusting that the compiler placed
those labels correctly. If operations occur that are not recognized, those operations
might not be guaranteed to protect their principals---for instance, an unlabeled call
might not protect the caller's data from the callee. On the flip side, applying an incorrect
label most likely means that the property becomes too strong to be enforced.

Otherwise, we do not assume that the code is reasonable\apt{still vague} or adheres to any particular
calling convention or source construct. In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism may place additional constraints, of course, particularly on the behavior of
call and return sequences.

@@

Security operations consist of calls (including tailcalls), returns,
allocations and deallocations. Calls and tailcalls identify the address of the call's target,
and the argument registers. Allocations and deallocations are phrased in terms of a pair
of an offset from the stack pointer and a size. Returns don't require any additional information.
%
\begin{align*}
  \psi \in \Psi ::= & \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{tailcall} ~ \addr_{target}  ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{return} & \\
  | & \mathbf{alloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
  | & \mathbf{dealloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
\end{align*}
%
Security principals are function activations: at any given time, pending activations
have security requirements that are recorded in a call stack, and the current
activation tracks context information that will inform its requirements when
it makes a call. Each activation has a {\it view}
of the system that maps each state element to a {\it security class}:
\[sc \in SEC ::= \sealed | \unsealed | \object | \public\]
\[V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\]

@@

\judgmenttwo{\(\mach \xrightarrow{\overline{\psi}} \mach', \obs \)}
            {\(\mathit{foldl} ~ (Op ~ \mach) ~ \context ~ \overline{\psi} = \context'\)}
            {\((\mach,\context) \stepstounder{\overline{\psi}} (\mach', \context', \obs)\)}

%\section{Calls, Returns, and Private Allocations}
\section{Examples}

In this section we consider a simple setting with calls, returns, and private allocations.
Figure \ref{fig:main} gives a C function {\tt main}, and its compiled RISC-V code,
that takes a secret in its arguments and initializes a variable to contain
potentially sensitive data.\apt{Arguments to {\tt main} are overly complicated.
  There's no need to match reality (and in fact {\tt argv} is really a {\tt char*}
  anyway).}\apt{As we discussed, it would be simpler to represent ``publish'' by
  writing to a specified global rather than with a call.}
It then calls another function {\tt f},
and afterward may decide to {\tt publish} its secret based on the contents of
its sensitive data. In this case, since {\tt sensitive} is initialized to 0,
it should not---instead it will publish the results of {\tt f}.
\apt{Would be better to use symbolic names instead of inetegers for {\tt jal}
  targets. Figure at bottom is good, but also needs additional labelling to
  show addresses relative to the new sp within {\tt f}.}

@@

Suppose that {\tt f} is not a (valid) C function at all, but an attacker seeking
to leak {\tt secret}! It might do so in a number of ways, shown as snippets of
assembly code in Figure \ref{fig:f}.
\apt{In (a,b), {\tt 12(sp)} maps to {\tt sensitive}, not {\tt secret} (I think!).
  It would be nice if (a) didn't have to push a frame (i.e. again by making publication
  just a global write) and if all the examples of {\tt f} were the same length, e.g.
  by adding {\tt nop}s.}

In Figure \ref{subfig:direct}, {\tt f} takes an offset from the stack
pointer, access {\tt secret}, and directly call {\tt publish} itself. But more
subtly, even if somehow prevented from outputting {\tt secret} directly, {\tt f}
instead return that value so that {\tt main} makes the call to {\tt publish},
as in Figure \ref{subfig:indirect}.

@@

\apt{This para is a bit of an orphan.}
At the start of execution the program counter is 0 and the stack pointer -4 \apt{or is it 0?},
with the stack growing down. The functions {\tt f} and {\tt publish}
are at addresses 100 and 200, respectively.

\apt{Need a smoother transition here. Be explicit that we are now going to start considering the security
  state.}

Figure \ref{fig:exec1} shows how the program counter, stack pointer, and context
develop over several steps, with labels on the steps that allocate space and then make
a call. \(\xrightarrow{\overline{\psi}}\) transitions are written \(\downarrow \overline{\psi}\) in this diagram;
events are omitted.\apt{graphics on right of figure need to be keyed to corresponding steps.}

@@

On a call, the formerly active principal's record is pushed onto the inactive list.
Its return target is the return address of the call, 
and the stack pointer target is the stack pointer at the moment of call.
The callee's view is updated from the caller's such that all \(\object\) locations
become \(\sealed\). (In more complex settings, objects that are intentionally passed
to the callee will not get sealed, but for now we assume no sharing of memory between activations.)
For registers, \(\overline{\reg_{args}}\) tells us which registers are used as arguments,
in this case {\tt a0}. These are mapped to \(\public\), while any non-argument, caller-saved
registers are mapped to \(\unsealed\). All callee-save registers are always \(\sealed\) and
the program counter \(\public\), as they were initialized.

On step \(n\), {\tt f} returns, and we restore the topmost inactive principal,
{\tt main}'s principal. \apt{This $n$ is a bit mysterious. Again, if all the snippets
  were the same length, you could use a concrete number here.}

\apt{Need a bridging sentence here, along the lines of: ``Now we consider how to define desirable
  stack safety properties that rule out various kinds of bad behavior.''}

@@

But what if {\tt f} returns to an unexpected place (i.e. \(\PCname \neq 20\) or \(\SP \neq -24\))\apt{-20?},
as would be the case in attack (d)? Then it has violated the WBCF property.
This property can be phrased in terms of a single step: for every transition
labeled as a return, the program counter and stack pointer at the next state
match those recorded in the top pending activation. The table in Figure \ref{fig:exec1}
assumes that WBCF is followed.

@@

In the case of the call from {\tt main} to {\tt f}, the \(\sealed\) elements are the
addresses -20 through -1 (allocated as private data) and callee-saved registers such as
the stack pointer and return address.
Note that the callee-saved registers may well have changed during the call---but if
so, the callee is obligated to restore them to their prior value.

One further caveat: it is possible that {\tt f} might overwrite {\tt main}'s data
in a way that is harmless---or that is rendered harmless by the enforcement mechanism!
\apt{This is still confusing, because the ``rendered harmless'' part applies just as much
  to the strict integrity we've been discussing up to now.}
This is the case in a lazy micro-policy\apt{presumes we've described these a bit in the introduction
  (which we should)}: the monitor permits the caller to write into the
callee's frame, but taints that write so that the callee cannot read it later without
triggering a failstop. In such a scenario we will consider a value {\it irrelevant}
if it could be replaced with any other value without changing the observable behavior
of the machine. More precisely, for a given state \(\mach\) and set of elements \(\components\),
we define a {\em \(\components\)-variant} state to be one agrees with \(\mach\) on every
element except those in \(\components\). The elements of \(\components\) are said to be
irrelevant in \(\mach\) if every variant state produces an equivalent trace
(see Section \ref{sec:events}.)

@@

Returning to our example: at step 4, when {\tt main} makes its call to {\tt f},
the call stack in the context is empty. It makes its call, and at step 5, {\tt main}'s
frame, including {\tt secret} and {\tt sensitive}, is mapped to \(\sealed\) from the
perspective of {\tt f}. So, the next time the call stack is empty (implicitly, when
we have returned to {\tt main}), elements of that frame must either match their
values at step 4, or be irrelevant to future computation.\apt{picture?}

@@

We treat confidentiality as a form of non-interference as well: the confidentiality of a caller
means that its callee's behavior is dependent only on publicly visible data,
not the caller's private state. \apt{Spell out the implications of this for initialization.}
As we saw in the examples, we must consider both the observable events
that the callee produces during the call and the changes that the callee makes to the state that might
affect the caller after the callee returns.

@@

Together, these definitions encompass the confidentiality of the caller from the callee.\apt{picture?}

@@

The forms of stack safety described above are largely independent of one another, and
can potentially be enforced separately in various combinations. This is important, because
many existing enforcement mechanisms enforce only some of the stack safety
properties. Stricter enforcement may have greater performance impacts, leading to decisions
about trade-offs between different degrees of stack safety.

@@

Others combine this protection with some degree of memory protection,
chiefly focusing on integrity. Skorstengaard et al. \cite{SkorstengaardSTK} characterize stack
safety as the combination of WBCF and {\it local state encapsulation} (LSE), and prove that their
capability-based enforcement satisfies both. LSE corresponds to integrity, plus some degree of
confidentiality.\apt{Be more explicit.}  They offer a fully abstract overlay semantics, which formalizes WBCF and LSE
together as a safe-by-construction abstract machine. That machine does not allow a callee to
read or write its caller's frame, but might allow it to read data that is left behind below
the caller's frame, which is weaker than our full caller confidentiality and rules out
callee confidentiality entirely. Georges et al. \cite{Georges22:TempsDesCerises} correct
both limitations.

@@

The intuition behind integrity (below) is that a caller may expect its
sealed data to be unchanged when control returns to it. In fact, the callee
may overwrite such data---when the data are found in callee-saved registers
this is perfectly legal---as long as it either restores it, or has some guarantee
that its changes will not impact the caller.

We start by defining a second-order logical operator
\(d \uparrow P\), pronounced ``\(P\) holds on return from depth \(d\),''
where \(P\) is a predicate on machine states. This is a coinductive relation
similar to ``weak until'' in temporal logic---it also holds if the program never
returns from depth \(d\).

@@

Similarly, for confidentiality, we will want to compare pairs of future states,
so we give a binary equivalent, \(d \Uparrow R\), where
\((\mach,\context) ~ (d \Uparrow R) ~ (\mach',\context')\) holds if \(R\) holds on the
first states that return from depth \(d\) after \((\mach,\context)\) and \((\mach',\context')\),
respectively. Once again, \(\Uparrow\) is coinductive.

@@

We now finally have everything we need to formalize our definitions for stack safety.
Figure \ref{fig:oprules} gives the operation rules for all of the operations we've described
so far.

@@

\definition A system enjoys {\it well-bracketed control flow} if 
\((\mach,(\_,(\_,\addr_{ret},\addr_{sp})) \stepstounder{\mathbf{return}} (\mach',\context,\obs)\)
implies \(\mach'[\PCname] = \addr_{ret}\) and \(\mach'[\SP] = \addr_{sp}\).

@@

\apt{These explanations that relate the definitions back to the example snippets are
  great. They would be even better if you can find a way to put them in Section II,
  based on (less formal) definitions of the terms introduced here.}

Consider again the attack in Figure \ref{subfig:WBCF}: the attacker adds
20 to the return address and then returns, thus bypassing the check and publishing
{\tt secret}. During the call step, we record in the context that the return to the
caller should have the program counter at the next instruction (address 20) and the
stack pointer restored to address -20. When the return occurs, we see that in the
state following it, the program counter is 40---a violation of WBCF.

To demonstrate why WBCF also cares about the stack pointer, consider an attack which
returns with the stack pointer at -12 instead of -20. Now, compare the layout of the stack relative
to the stack pointer as it should be (top) to the one that results by increasing the
stack pointer before return (bottom):

@@

\apt{I think it might be clearer just to have one row with the two different SP pointers
  (the proper one and the bad one) marked.}

@@

There is an alternative foramlization of well-bracketed control flow using \(\uparrow\).

\definition For a machine state \(\mach\), let
\(ret ~ (\mach,\context) = \{\mach' \mid \mach'[\SP] = \mach[\SP] \land \mach'[\PCname] = \mach[\PCname]\}\).
\apt{Note: you'll get better spacing by using $\mid$ rather than $|$ in set comprehensions.}
A system enjoys  well-bracketed control flow if
\((\mach,\context) \stepstounder{\overline{\psi}} (\mach',(V,\sigma),\obs)\) where 
\(\mathbf{call} ~ \addr ~ \overline{\reg} ~ \overline{sa} \in \psi\) or
\(\mathbf{tailcall} ~ \addr ~ \overline{\reg} ~ \overline{sa} \in \psi\)
implies \(|\sigma| \uparrow ret(\mach')\).

@@

\apt{Sudden appearance of $\mathbf{tailcall}$??}
Once again we can think about our example attack. When the call occurs,
we define a predicate \(ret ~ (\mach,\context)\) on states that holds when the program counter
and stack pointer have the appropriate values. Then we use apply the \(\uparrow\)
operator to this predicate with the depth of the call stack {\it after the call} and
the machine state {\it before the call}.

After the call, the size of the call stack, \(|\sigma|\), is one greater than it was before the call,
and if the callee makes further calls, it will continue to be incremented.
Similarly, each return will decrement it, until it is finally lower than in the
initial state. This is the return that matches the original call, and so
the resulting state is when we require \(ret(\mach)\) to hold.

@@

\definition Let \((\mach,\context)\) be a combined state with
\(\context = (V,\sigma)\), and
\(\components = \{\component \mid V ~ \component = \sealed\}\).
Let \(P ~ (\mach',\context')\) be a predicate that holds on a state
\(\Delta(\mach,\mach')\) is irrelevant in \((\mach', \context')\).\apt{Something is broken here!}
Then \(\mach\) enjoys {\it return-time integrity} if \(|\sigma| \uparrow P\) holds
on \((\mach,\context)\).

@@

\definition The {\em corrupted set} \(\bar{\Diamond}(\mach,\mach',\nach,\nach')\)
of four states treats \(\mach\) and \(\nach\) as the initial states and
\(\mach'\) and \(\nach'\) as their corresponding final states, and is the
set of elements that were corrupted between them. That is, the set of all elements
\(\component \in \Delta(\mach,\mach') \cup \Delta(\nach,\nach')\) such that
\(\mach'[\component] \not = \nach'[\component]\). ]\apt{Define first, explain after.}

\definition Let \((\mach,\context)\) be a state with \(\context = (V,\sigma)\), and
\(\components = \{\component \mid V ~ \component \in \{\sealed, \unsealed\}\}\).
Then \((\mach,\context)\) enjoys {\it internal confidentiality} with respect to \apt{??}
if, for any \(\nach\) that is a \(\components\)-variant of \(\mach\), we can take
\(|\sigma| \uparrow (\mach,\context) \hookrightarrow \obsT\) and
\(|\sigma| \uparrow (\nach,\context) \hookrightarrow \obsT'\) and have that
\(\obsT \simeq \obsT'\).

\definition Let \((\mach,\context)\) be a state with \(\context = (V,\sigma)\),
and \(\components = \{\component \mid V ~ \component \in \{\sealed, \unsealed\}\}\).
Let \(\nach\) be a \(\components\)-variant of \(\mach\).
Let \(R\) be a relation such that \((\mach_1,\context_1) ~ R ~ (\mach_2,\context_2)\)
if \(\bar{\Diamond}(\mach,\mach_1,\nach,\mach_2)\) is irrelevant in \((\mach_1,\context_1)\).
Then \((\mach,\context)\) enjoys {\it return-time confidentiality}
if, for any such \(\nach\), \((\mach,\context) ~ (|\sigma| \Uparrow R) ~ (\nach,\context)\).

@@

\definition Let \((\mach,\context)\) be a state with \(\context = (V,\sigma)\), and
\(\components = \{\component \mid V ~ \component = \unsealed\}\).
Let \(P\) be a predicate that holds on a state \((\mach',\context')\) if
\(\mach' ~ \parallel ~ \Delta(\mach,\mach') \cap \components\).
Then \(\mach\) enjoys {\it post-return confidentiality} if \(|\sigma| \downarrow P\) holds.

@@

When the callee in such a scenario makes a call of its own, the objects passed to it
will in turn be sealed---unless it passes them on, which can happen with pass-by-reference
arguments!

@@

In order to express such a property, we need our machine to carry some notion
of {\it pointer provenance}---a distinction between a pointer that is intended to
point to a given object, and non-pointer integers as well as pointers to other objects.
Then \(\mathit{passed}\) should recursively identify all objects that
are reachable transitively from valid pointers in registers and accessible memory;
these keep their \(\object\) status, while those that are not reachable become \(\sealed\).
